Concurrent Programming with CXL

### 2020-06-22 book/paper.tex
Working on starvation solution

In this chapter, we will present a version of a reader/writer lock
implementation that solves this type of starvation.
In particular, the probability that either a reader or writer gets starved
will be exponentially diminishing.
We shall call such a solution \emph{fair}
\index{fairness}
(although it does not quite
match the usual formal nor vernacular concepts of fairness).
\glsadd{fairness}

>>>>

In this chapter, we will present two SBS-based reader/writer lock
implementations that solves this type of starvation.
SBS allow much control over which thread runs next and is therefore a
good starting point for developing synchronization algorithms that do not
suffer from starvation.
For the first solution the probability that either a reader or writer gets starved
will be exponentially diminishing.
We shall call such a solution \emph{fair}
\index{fairness}
(although it does not quite
match the usual formal nor vernacular concepts of fairness).
\glsadd{fairness}
